---
title: "Depression vs Revelry (Sex, Drugs, Alcohol)"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Downloading and installing relevant libraries
```{r}
if(!require("ggplot2")) install.packContextAges("ggplot2", repos='https://cran.ma.imperial.ac.uk/')
if(!require("summarytools")) install.packContextAges("summarytools", repos='https://cran.ma.imperial.ac.uk/')
if(!require("knitr")) install.packContextAges("knitr", repos='https://cran.ma.imperial.ac.uk/')
if(!require("kableExtra")) install.packContextAges("kable", repos='https://cran.ma.imperial.ac.uk/')
if(!require("broom")) install.packContextAges("broom", repos='https://cran.ma.imperial.ac.uk/')
if(!require("fRegression")) install.packContextAges("fRegression", repos='https://cran.ma.imperial.ac.uk/')
if(!require("sandwich")) install.packContextAges("sandwich", repos='https://cran.ma.imperial.ac.uk/')
if(!require("lmtest")) install.packContextAges("lmtest", repos='https://cran.ma.imperial.ac.uk/')
if(!require("pander")) install.packContextAges("pander", repos='https://cran.ma.imperial.ac.uk/')
if(!require("stargazer")) install.packContextAges("stargazer", repos='https://cran.ma.imperial.ac.uk/')
if(!require("dplyr")) install.packContextAges("dplyr", repos='https://cran.ma.imperial.ac.uk/')
if(!require("rcompanion")) install.packContextAges("rcompanion", repos='https://cran.ma.imperial.ac.uk/')
if(!require("corrplot")) install.packContextAges("corrplot", repos='https://cran.ma.imperial.ac.uk/')
if(!require("caret")) install.packContextAges("caret", repos='https://cran.ma.imperial.ac.uk/')
if(!require("formatR")) install.packContextAges("formatR", repos='https://cran.ma.imperial.ac.uk/')
if(!require("neuralnet")) install.packContextAges("neuralnet", repos='https://cran.ma.imperial.ac.uk/')

library(neuralnet)
library(formatR)
library(caret)
library(corrplot)
library(ggplot2)
library(summarytools)
library(dplyr) 
library(broom)
library(stargazer)
library(fRegression) 
library(sandwich) 
library(lmtest)
library(pander)
library(rcompanion)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE)
```

# Loading and merging wave 1 data and context data
```{r}
load("21600-0001-Data.rda")
load("21600-0002-Data.rda")
data_all_1 <- merge(da21600.0001,da21600.0002,by="AID")
```

# Selecting relevant columns and renaming to understandable terms
```{r}
#Cleaning descriptors data by only keeping relevant columns and renaming them 
data_all_1 <- data_all_1 %>% select("AID","BIO_SEX", "H1GI6A","BST90P05", "BST90P13","BST90P15","BST90P19","BST90P20", "H1GI1Y", "H1FS6", "H1CO1", "PA55", "PA12","H1GH28", "H1TO15", "H1TO40"  )

data_all_1 <- data_all_1 %>% rename( Sex = BIO_SEX ,Race = H1GI6A, ContextSex = BST90P05,  ContextHouseType = BST90P13, ContextHouseInc = BST90P15, ContextPoor = BST90P19, ContextEduc = BST90P20, Year = H1GI1Y, Intercourse = H1CO1, Depressed = H1FS6,  Income_thousands = PA55, EducationLevel = PA12, Weight = H1GH28, Alcohol = H1TO15, Drugs = H1TO40)

head(data_all_1)
```

# Cleaning data by removing the (x)(y) precursors to every answer
```{r}
data_all_1[,c("Sex")] <- substring(data_all_1[,c("Sex")],9)
data_all_1[,c("Race")] <- substring(data_all_1[,c("Race")],9)
data_all_1[,c("ContextSex")] <- substring(data_all_1[,c("ContextSex")],9)
data_all_1[,c("ContextHouseType")] <- substring(data_all_1[,c("ContextHouseType")],9)
data_all_1[,c("ContextPoor")] <- substring(data_all_1[,c("ContextPoor")],9)
data_all_1[,c("ContextEduc")] <- substring(data_all_1[,c("ContextEduc")],9)
data_all_1[,c("Depressed")] <- substring(data_all_1[,c("Depressed")],9)
data_all_1[,c("Intercourse")] <- substring(data_all_1[,c("Intercourse")],9)
data_all_1[,c("EducationLevel")] <- substring(data_all_1[,c("EducationLevel")],9)
data_all_1[,c("Weight")] <- substring(data_all_1[,c("Weight")],9)
data_all_1[,c("Alcohol")] <- substring(data_all_1[,c("Alcohol")],9)
data_all_1[,c("Drugs")] <- substring(data_all_1[,c("Drugs")],10)
data_all_1[,c("Year")] <- substring(data_all_1[,c("Year")],11)
data_all_1$Age <- with(data_all_1, (1995-as.numeric(Year)))
head(data_all_1)
summary(data_all_1)
```

# Filtering down data to just Under 18 year olds
```{r}
#Filtering data
data_all_1 <- data_all_1 %>% filter(Age < 18)
head(data_all_1)
```

# Count number of complete records in the dataset and assign non - na dataset for comparison 
```{r}
data_all_nona <- na.omit(data_all_1)
head(data_all_nona)
```

# Visualising the data pre - cleansing
```{r}
# We create the table of frequencies of different values for ContextRace
Race_data = data_all_1[,c("Race")]
Race_frequency <- table(Race_data, useNA = "always");

# We create a table with extracted frequencies, values and provided labels 
Race_data_frame <- as.data.frame(Race_frequency); 

# For creating chart, we need to use ggplot() function and provide input data for each axes. # Then we use geom_bar() function to apply bar chart specifications and # labs() function to put labels on the chart. theme() function has been used to move the title to the center.
ggplot(data = Race_data_frame, mapping = aes(x = Race_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#same but for all other variables
#ContextSex
ContextSex_data = data_all_1[,c("ContextSex")]
ContextSex_frequency <- table(ContextSex_data, useNA = "always");
ContextSex_data_frame <- as.data.frame(ContextSex_frequency); 
ggplot(data = ContextSex_data_frame, mapping = aes(x = ContextSex_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#ContextHouseType
ContextHouseType_data = data_all_1[,c("ContextHouseType")]
ContextHouseType_frequency <- table(ContextHouseType_data, useNA = "always");
ContextHouseType_data_frame <- as.data.frame(ContextHouseType_frequency); 
ggplot(data = ContextHouseType_data_frame, mapping = aes(x = ContextHouseType_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#ContextHouseInc
ContextHouseInc_data = data_all_1[,c("ContextHouseInc")]
ContextHouseInc_frequency <- table(ContextHouseInc_data, useNA = "always");
ContextHouseInc_data_frame <- as.data.frame(ContextHouseInc_frequency); 
ggplot(data = ContextHouseInc_data_frame, mapping = aes(x = ContextHouseInc_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#contextpoor
contextpoor_data = data_all_1[,c("ContextPoor")]
contextpoor_frequency <- table(contextpoor_data, useNA = "always");
contextpoor_data_frame <- as.data.frame(contextpoor_frequency); 
ggplot(data = contextpoor_data_frame, mapping = aes(x = contextpoor_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#contexteduc
contexteduc_data = data_all_1[,c("ContextEduc")]
contexteduc_frequency <- table(contexteduc_data, useNA = "always");
contexteduc_data_frame <- as.data.frame(contexteduc_frequency); 
ggplot(data = contexteduc_data_frame, mapping = aes(x = contexteduc_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#depressed
depressed_data = data_all_1[,c("Depressed")]
depressed_frequency <- table(depressed_data, useNA = "always");
depressed_data_frame <- as.data.frame(depressed_frequency); 
ggplot(data = depressed_data_frame, mapping = aes(x = depressed_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#intercourse
intercourse_data = data_all_1[,c("Intercourse")]
intercourse_frequency <- table(intercourse_data, useNA = "always");
intercourse_data_frame <- as.data.frame(intercourse_frequency); 
ggplot(data = intercourse_data_frame, mapping = aes(x = intercourse_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#sex
sex_data = data_all_1[,c("Sex")]
sex_frequency <- table(sex_data, useNA = "always");
sex_data_frame <- as.data.frame(sex_frequency); 
ggplot(data = sex_data_frame, mapping = aes(x = sex_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#income
income_data = data_all_1[,c("Income_thousands")]
income_frequency <- table(income_data, useNA = "always");
income_data_frame <- as.data.frame(income_frequency); 
ggplot(data = income_data_frame, mapping = aes(x = income_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#weight
weight_data = data_all_1[,c("Weight")]
weight_frequency <- table(weight_data, useNA = "always");
weight_data_frame <- as.data.frame(weight_frequency); 
ggplot(data = weight_data_frame, mapping = aes(x = weight_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#alcohol
alcohol_data = data_all_1[,c("Alcohol")]
alcohol_frequency <- table(alcohol_data, useNA = "always");
alcohol_data_frame <- as.data.frame(alcohol_frequency); 
ggplot(data = alcohol_data_frame, mapping = aes(x = alcohol_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#drugs
drug_data = data_all_1[,c("Drugs")]
drug_frequency <- table(drug_data, useNA = "always");
drug_data_frame <- as.data.frame(drug_frequency); 
ggplot(data = drug_data_frame, mapping = aes(x = drug_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#educ
educ_data = data_all_1[,c("EducationLevel")]
educ_frequency <- table(educ_data, useNA = "always");
educ_data_frame <- as.data.frame(educ_frequency); 
ggplot(data = educ_data_frame, mapping = aes(x = educ_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#age
age_data = data_all_1[,c("Age")]
age_frequency <- table(age_data, useNA = "always");
age_data_frame <- as.data.frame(age_frequency); 
ggplot(data = age_data_frame, mapping = aes(x = age_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Data cleansing - removing NA's and assigning to relevant groups
```{r}
#Replace NA's
data_all_1$ContextSex[is.na(data_all_1$ContextSex)] <- "Heavily female"
data_all_1$ContextHouseType[is.na(data_all_1$ContextHouseType)] <- "Non-family household"
data_all_1$ContextHouseInc[is.na(data_all_1$ContextHouseInc)] <- 30309 
data_all_1$ContextPoor[is.na(data_all_1$ContextPoor)] <- "High"
data_all_1$ContextEduc[is.na(data_all_1$ContextEduc)] <- "No high school or equivalency"
data_all_1$Income_thousands[is.na(data_all_1$Income_thousands)] <- 47.7
data_all_1$EducationLevel[is.na(data_all_1$EducationLevel)] <- 0 
data_all_1$Alcohol[is.na(data_all_1$Alcohol)] <- "Never (skip to Q29)"
data_all_1$Intercourse[is.na(data_all_1$Intercourse)] <- "No (skip to next section)"
data_all_1$Drugs[is.na(data_all_1$Drugs)] <- "1 year"
data_all_1$Weight[is.na(data_all_1$Weight)] <- "Very overweight"
data_all_1$Age[is.na(data_all_1$Age)] <- 16.04

#Remove NA's for Depressed
data_all_1 <- na.omit(data_all_1)
head(data_all_1)
```

# Visualising the context data post cleanse
```{r}
#Race
Race_data = data_all_1[,c("Race")]
Race_frequency <- table(Race_data);
Race_data_frame <- as.data.frame(Race_frequency); 
ggplot(data = Race_data_frame, mapping = aes(x = Race_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#ContextSex
ContextSex_data = data_all_1[,c("ContextSex")]
ContextSex_frequency <- table(ContextSex_data);
ContextSex_data_frame <- as.data.frame(ContextSex_frequency); 
ggplot(data = ContextSex_data_frame, mapping = aes(x = ContextSex_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#ContextHouseType
ContextHouseType_data = data_all_1[,c("ContextHouseType")]
ContextHouseType_frequency <- table(ContextHouseType_data);
ContextHouseType_data_frame <- as.data.frame(ContextHouseType_frequency); 
ggplot(data = ContextHouseType_data_frame, mapping = aes(x = ContextHouseType_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#ContextHouseInc
ContextHouseInc_data = data_all_1[,c("ContextHouseInc")]
ContextHouseInc_frequency <- table(ContextHouseInc_data);
ContextHouseInc_data_frame <- as.data.frame(ContextHouseInc_frequency); 
ggplot(data = ContextHouseInc_data_frame, mapping = aes(x = ContextHouseInc_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#contextpoor
contextpoor_data = data_all_1[,c("ContextPoor")]
contextpoor_frequency <- table(contextpoor_data);
contextpoor_data_frame <- as.data.frame(contextpoor_frequency); 
ggplot(data = contextpoor_data_frame, mapping = aes(x = contextpoor_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#contexteduc
contexteduc_data = data_all_1[,c("ContextEduc")]
contexteduc_frequency <- table(contexteduc_data);
contexteduc_data_frame <- as.data.frame(contexteduc_frequency); 
ggplot(data = contexteduc_data_frame, mapping = aes(x = contexteduc_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#depressed
depressed_data = data_all_1[,c("Depressed")]
depressed_frequency <- table(depressed_data);
depressed_data_frame <- as.data.frame(depressed_frequency); 
ggplot(data = depressed_data_frame, mapping = aes(x = depressed_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#intercourse
intercourse_data = data_all_1[,c("Intercourse")]
intercourse_frequency <- table(intercourse_data);
intercourse_data_frame <- as.data.frame(intercourse_frequency); 
ggplot(data = intercourse_data_frame, mapping = aes(x = intercourse_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#income
income_data = data_all_1[,c("Income_thousands")]
income_frequency <- table(income_data);
income_data_frame <- as.data.frame(income_frequency); 
ggplot(data = income_data_frame, mapping = aes(x = income_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#weight
weight_data = data_all_1[,c("Weight")]
weight_frequency <- table(weight_data);
weight_data_frame <- as.data.frame(weight_frequency); 
ggplot(data = weight_data_frame, mapping = aes(x = weight_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#sex
sex_data = data_all_1[,c("Sex")]
sex_frequency <- table(sex_data);
sex_data_frame <- as.data.frame(sex_frequency); 
ggplot(data = sex_data_frame, mapping = aes(x = sex_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#alcohol
alcohol_data = data_all_1[,c("Alcohol")]
alcohol_frequency <- table(alcohol_data);
alcohol_data_frame <- as.data.frame(alcohol_frequency); 
ggplot(data = alcohol_data_frame, mapping = aes(x = alcohol_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#drugs
drug_data = data_all_1[,c("Drugs")]
drug_frequency <- table(drug_data);
drug_data_frame <- as.data.frame(drug_frequency); 
ggplot(data = drug_data_frame, mapping = aes(x = drug_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#educ
educ_data = data_all_1[,c("EducationLevel")]
educ_frequency <- table(educ_data);
educ_data_frame <- as.data.frame(educ_frequency); 
ggplot(data = educ_data_frame, mapping = aes(x = educ_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

#age
age_data = data_all_1[,c("Age")]
age_frequency <- table(age_data);
age_data_frame <- as.data.frame(age_frequency); 
ggplot(data = age_data_frame, mapping = aes(x = age_data, y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Matrices of Responses for depressed vs intercourse, drugs, and alcohol
```{r}
#frequency
data = data_all_1[,c("Depressed","Intercourse")]
frequency <- table(data);
frequency

#frequency
data = data_all_1[,c("Depressed","Drugs")]
frequency <- table(data);
frequency

#frequency
data = data_all_1[,c("Depressed","Alcohol")]
frequency <- table(data);
frequency
```


#Changing reponses to binary where applicable (all apart from Age) - for both the dataset and the na removed dataset for comparison
```{r}
data_all_1 = within(data_all_1, {
    DepressedBin = ifelse(Depressed == "A lot of the time" | Depressed == "Most/all of the time" , 1, 0)
    CIncRichAreaBin = ifelse(ContextHouseInc >= 38000,1,0)
    CIncAvgAreaBin = ifelse(ContextHouseInc < 38000 & ContextHouseInc >= 20000,1,0)
    CSexBin = ifelse(ContextSex == "Balanced",1,0)
    CHouseTypeBin = ifelse(ContextHouseType == "Married couple family household", 1,0)
    CPoorBin = ifelse(ContextPoor == "High",1,0)
    CEducBin = ifelse(ContextEduc == "College degree or more" | ContextEduc == "High school degree/no college degree", 1, 0)
    IncRichBin = ifelse(Income_thousands >= 60,1,0)
    IncAvgBin = ifelse(Income_thousands < 60 & Income_thousands >= 22,1,0)
    IntercourseBin = ifelse(Intercourse == "Yes" ,1,0)
    EducLvlBin = ifelse(grepl("Prof training beyond", EducationLevel) | grepl("Business", EducationLevel) | grepl("High school graduate", EducationLevel) | grepl("Graduated", EducationLevel) | grepl("Completed", EducationLevel) | grepl("College", EducationLevel),1,0)
    AlcoholBin = ifelse(grepl("Never", Alcohol) | Alcohol == 0,0,1)
    DrugsBin = ifelse(grepl("You never tried any other type of illegal drug", Drugs),0,1)
    WeightBin = ifelse(grepl("About the", Weight) ,1,0)
    RaceBin = ifelse(Race == "Marked" , 1, 0)
    SexBin = ifelse(Sex == "Male" , 1, 0)
 })

data_all_nona = within(data_all_nona, {
    DepressedBin = ifelse(Depressed == "A lot of the time" | Depressed == "Most/all of the time" , 1, 0)
    CIncRichAreaBin = ifelse(ContextHouseInc >= 38000,1,0)
    CIncAvgAreaBin = ifelse(ContextHouseInc < 38000 & ContextHouseInc >= 20000,1,0)
    CSexBin = ifelse(ContextSex == "Balanced",1,0)
    CHouseTypeBin = ifelse(ContextHouseType == "Married couple family household", 1,0)
    CPoorBin = ifelse(ContextPoor == "High",1,0)
    CEducBin = ifelse(ContextEduc == "College degree or more" | ContextEduc == "High school degree/no college degree", 1, 0)
    IncRichBin = ifelse(Income_thousands >= 60,1,0)
    IncAvgBin = ifelse(Income_thousands < 60 & Income_thousands >= 22,1,0)
    IntercourseBin = ifelse(Intercourse == "Yes" ,1,0)
    EducLvlBin = ifelse(grepl("Prof training beyond", EducationLevel) | grepl("Business", EducationLevel) | grepl("High school graduate", EducationLevel) | grepl("Graduated", EducationLevel) | grepl("Completed", EducationLevel) | grepl("College", EducationLevel),1,0)
    AlcoholBin = ifelse(grepl("Never", Alcohol) | Alcohol == 0,0,1)
    DrugsBin = ifelse(grepl("You never tried any other type of illegal drug", Drugs),0,1)
    WeightBin = ifelse(grepl("About the", Weight) ,1,0)
    RaceBin = ifelse(Race == "Marked" , 1, 0)
    SexBin = ifelse(Sex == "Male" , 1, 0)
 })
```


# Matrices of Binary Responses for all variables against depressed
```{r}
#frequency
data = data_all_1[,c("DepressedBin","IntercourseBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","RaceBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","CIncRichAreaBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","CIncAvgAreaBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","CSexBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","CHouseTypeBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","CPoorBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","IncRichBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","IncAvgBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","CEducBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","AlcoholBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","WeightBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","SexBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","DrugsBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)

#frequency
data = data_all_1[,c("DepressedBin","EducLvlBin")]
frequency <- table(data);
frequency
rcompanion::cramerV(frequency)
```

# Correlation Matrix data extraction
```{r}
corr_data <- data_all_1[,c("DepressedBin","IntercourseBin","AlcoholBin","DrugsBin", "Age","SexBin","RaceBin","WeightBin","IncRichBin","IncAvgBin","EducLvlBin","CIncRichAreaBin","CIncAvgAreaBin","CHouseTypeBin","CPoorBin","CSexBin","CEducBin")]
head(corr_data)

corr_data_nona <- data_all_nona[,c("DepressedBin","IntercourseBin","AlcoholBin","DrugsBin", "Age","SexBin","RaceBin","WeightBin","IncRichBin","IncAvgBin","EducLvlBin","CIncRichAreaBin","CIncAvgAreaBin","CHouseTypeBin","CPoorBin","CSexBin","CEducBin")]
head(corr_data_nona)
```

# Correlation Matrix production
```{r}
mcor <- round(cor(corr_data, method = c("pearson", "kendall", "spearman")),3)
mcor

jpeg("Plot.jpeg", width = 9, height = 9, units = 'in', res = 4000)
corrplot.mixed(mcor,  tl.pos = "l", tl.cex = .8, lower = "number", upper = "color", lower.col  = "black", number.cex = .5 ,  tl.col = "black", order = "hclust", tl.srt = 45)
```

# Run regressions against both the cleansed dataset and non-na dataset
```{r}
# Regression against cleansed dataset
ols <- lm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , data = data_all_1);
logit <- glm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , family = binomial(link = "logit"), data = data_all_1);
probit <- glm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , family = binomial(link = "probit"), data = data_all_1);

stargazer(ols, logit, probit, 
          type = "text", 
          column.labels = c("Linear","Logit","Probit"), 
          single.row = TRUE,
          align = TRUE)

# Regressions against non-na dataset
ols <- lm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , data = data_all_nona);
logit <- glm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , family = binomial(link = "logit"), data = data_all_nona);
probit <- glm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , family = binomial(link = "probit"), data = data_all_nona);

stargazer(ols, logit, probit, 
          type = "text", 
          column.labels = c("Linear","Logit","Probit"), 
          single.row = TRUE,
          align = TRUE)
```

# Machine Learning - Neural Network

# Split data into train and test (80% into train)
```{r}
#Filtering data
data_depressed <- data_all_1 %>% filter(DepressedBin == 1)
head(data_depressed)
data_notdepressed <- data_all_1 %>% filter(DepressedBin == 0)
head(data_notdepressed)

#train_depressed
train_dep_ind <- sample(seq_len(nrow(data_depressed)), size = floor(nrow(data_depressed) * 0.8))
train_dep <- data_depressed[train_dep_ind,]
head(train_dep)
test_dep <- data_depressed[-train_dep_ind,]
head(test_dep)

#train_depressed
train_nondep_ind <- sample(seq_len(nrow(data_notdepressed)), size = floor(nrow(data_notdepressed) * 0.8))
train_nondep <- data_notdepressed[train_nondep_ind,]
head(train_nondep)
test_nondep <- data_notdepressed[-train_nondep_ind,]
head(test_nondep)

train <- rbind(train_dep,train_nondep)
test <- rbind(test_dep,test_nondep)
head(train)
head(test)
```

# Train logit based on train data to compare to neural network
```{r}
#Building model based on test dataset
logit <- glm(DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin , family = binomial(link = "logit"), data = train)

#Predicting values
prob <- predict(logit,test)
pred <- ifelse(prob >0.5,1,0)

#Confusion Matrix
table(factor(pred, levels=min(test$DepressedBin):max(test$DepressedBin)), 
      factor(test$DepressedBin, levels=min(test$DepressedBin):max(test$DepressedBin)))
```



# Build Neural Network
```{r}
nn = neuralnet(formula = DepressedBin ~  IntercourseBin + AlcoholBin + DrugsBin + Age + SexBin + RaceBin + WeightBin  + IncRichBin + IncAvgBin + EducLvlBin + CIncRichAreaBin + CIncAvgAreaBin + CHouseTypeBin + CPoorBin + CSexBin + CEducBin, 
               data = train,
               hidden = 2, 
               act.fct = "logistic",
               linear.output=FALSE, 
               err.fct = 'sse')
```

# Summary and Error Statistics
```{r}
summary(nn)

nn$result.matrix['error',]
```

# Neural Network visualisations
```{r}
plot(nn)
```

# Predict based on Neural Network
```{r}
#fit model using test dataset
Predict <- neuralnet::compute(nn,test)

#probabilities
prob <- Predict$net.result

#back to binary variables
pred <- ifelse(prob>0.5, 1, 0)

#confusion matrix
table(factor(pred, levels=min(test$DepressedBin):max(test$DepressedBin)), 
      factor(test$DepressedBin, levels=min(test$DepressedBin):max(test$DepressedBin)))
```